% ============================================================================
% How to Use This Study Guide — Grade 7
% Hexagon-badged numbered steps with clean info panels.
% UNIQUE to Study Guide: hexagon badges, teal brand, info panels.
% Distinct from Workbook (diamond badges, blue brand, dash-box panels).
% ============================================================================

\thispagestyle{empty}

{
\sffamily

% ── Header ────────────────────────────────────────────────────────────────
\sgPageHeader{How to Use This Study Guide}{Four steps to master every topic.}

% ── Hex Steps ─────────────────────────────────────────────────────────────
\begin{center}
\begin{minipage}{0.84\textwidth}

\sgHexStep{1}{funTeal}{Read the Concept}{%
    Each topic opens with a clear explanation of the key idea or rule.
    Read it carefully --- understanding \emph{why} a method works is just
    as important as knowing how to use it.}

\sgHexStep{2}{funBlue}{Study the Examples}{%
    Worked examples walk through each problem type step by step.
    Follow along with pencil and paper. Try covering the solution
    and solving it yourself before you look.}

\sgHexStep{3}{funOrange}{Practice on Your Own}{%
    Every section ends with practice problems that mirror the examples.
    Write out all your steps --- messy work is fine as long as your
    thinking is visible.}

\sgHexStep{4}{funPurple}{Check and Correct}{%
    Flip to the Answer Key and compare every answer. When you find a
    mistake, figure out \emph{where} your reasoning went wrong.
    Then try a similar problem again. That's how real mastery happens.}

\end{minipage}
\end{center}

\vspace{4mm}

% ── Study Routine ─────────────────────────────────────────────────────────
\begin{center}
\begin{minipage}{0.84\textwidth}
\begin{sgInfoPanel}{funTeal}
    {\bfseries\color{funTealDark}\faCalendar\hspace{2mm}Suggested Study Routine}

    \vspace{3mm}

    \begin{itemize}[leftmargin=1.2em, itemsep=2pt]
        \item[\textcolor{funTealDark}{\faAngleDoubleRight}]
            \textbf{Weekdays:} Study one topic per day
            (about 20--30 minutes).
        \item[\textcolor{funTealDark}{\faAngleDoubleRight}]
            \textbf{End of week:} Review your notes and redo any
            problems you missed.
        \item[\textcolor{funTealDark}{\faAngleDoubleRight}]
            \textbf{Before a test:} Use the Math Quick Reference
            on the next page for a fast refresher.
    \end{itemize}
\end{sgInfoPanel}
\end{minipage}
\end{center}

\vspace{4mm}

% ── Pair It Up ────────────────────────────────────────────────────────────
\begin{center}
\begin{minipage}{0.84\textwidth}
\begin{sgInfoPanel}{funGreen}
    {\bfseries\color{funGreenDark}\faLink\hspace{2mm}Pair It Up}

    \vspace{2mm}

    This study guide covers the \emph{what} and \emph{how}. For extra
    drill, pair it with the \textit{Grade~7 Math Workbook} ---
    hundreds of additional practice problems organised by the same
    chapters and topics.
\end{sgInfoPanel}
\end{minipage}
\end{center}

\vspace{4mm}

% ── For Parents & Teachers ────────────────────────────────────────────────
\begin{center}
\begin{minipage}{0.84\textwidth}
\begin{sgInfoPanel}{funOrange}
    {\bfseries\color{funOrangeDark}\faUsers\hspace{2mm}For Parents \& Teachers}

    \vspace{2mm}

    \begin{itemize}[leftmargin=1.2em, itemsep=2pt]
        \item[\textcolor{funOrangeDark}{\faAngleDoubleRight}]
            Encourage students to explain concepts in their own words.
        \item[\textcolor{funOrangeDark}{\faAngleDoubleRight}]
            Keep study sessions to 20--30 minutes for best focus.
        \item[\textcolor{funOrangeDark}{\faAngleDoubleRight}]
            Celebrate effort and progress, not just correct answers.
    \end{itemize}
\end{sgInfoPanel}
\end{minipage}
\end{center}

}

\clearpage
