% Post-Test 11 — Mid-Point Check-In: Halfway 5-test reflection
\clearpage
\thispagestyle{empty}
{\sffamily

\begin{center}
{\fontsize{22}{26}\selectfont\bfseries\color{funTeal} \faMapSigns\hspace{3mm}Halfway Check-In\hspace{3mm}\faMapSigns}

\vspace{2mm}
{\color{funGray}\hrulefill}
\end{center}

\vspace{3mm}

\begin{tcolorbox}[
    enhanced,
    colback=funTealLight,
    colframe=funTeal!50,
    arc=10pt,
    boxrule=1.5pt,
    left=6mm, right=6mm, top=5mm, bottom=5mm,
]
{\large\bfseries\color{funTealDark} \faFlagCheckered\hspace{2mm}150 Questions Done --- Halfway There!}

\vspace{2mm}

You've reached the midpoint. Time for an honest self-assessment. Check the box that fits:

\vspace{3mm}

\begin{itemize}[leftmargin=6mm, itemsep=4pt]
    \item[$\square$] I'm feeling more confident than when I started
    \item[$\square$] I've found strategies that work for me
    \item[$\square$] I can identify my mistake types (careless / concept / misread)
    \item[$\square$] I know which topics need the most work
    \item[$\square$] I'm managing my time better
\end{itemize}

\vspace{2mm}

\textbf{My biggest strength:} \rule[-2pt]{6cm}{0.5pt}

\vspace{2mm}

\textbf{My biggest area to improve:} \rule[-2pt]{5cm}{0.5pt}
\end{tcolorbox}

\vspace{3mm}

\begin{tcolorbox}[
    enhanced,
    colback=funYellowLight,
    colframe=funYellow!60,
    arc=10pt,
    boxrule=1pt,
    left=6mm, right=6mm, top=4mm, bottom=4mm,
]
{\bfseries\color{funYellowDark} \faLightbulb\hspace{2mm}The Second Half}

\vspace{2mm}

You have 4 tests left. That's 120 more questions to sharpen your skills. Use what you've learned so far and go into the second half with a plan. You're doing great!
\end{tcolorbox}

\vspace{4mm}

\begin{center}
{\large\bfseries\color{funTealDark} \faMountain\hspace{2mm}Halfway up the mountain. Keep climbing!\hspace{2mm}\faMountain}
\end{center}

}
\newpage
