% Pre-Test 08 — Two-Pass Method: Easy first, hard second
\clearpage
\thispagestyle{empty}
{\sffamily

\begin{center}
{\fontsize{22}{26}\selectfont\bfseries\color{funGreen} \faSync\hspace{3mm}The Two-Pass Method\hspace{3mm}\faSync}

\vspace{2mm}
{\color{funGray}\hrulefill}
\end{center}

\vspace{3mm}

\begin{tcolorbox}[
    enhanced,
    colback=funGreenLight,
    colframe=funGreen!50,
    arc=10pt,
    boxrule=1.5pt,
    left=6mm, right=6mm, top=5mm, bottom=5mm,
]
{\large\bfseries\color{funGreenDark} \faRoute\hspace{2mm}A Smarter Way to Take a Test}

\vspace{2mm}

Imagine you're at a buffet. You wouldn't spend 10 minutes deciding on one dish while the line moves — you'd grab the ones you love first, then go back for the rest. Tests work the same way!

\vspace{4mm}

\textbf{\textcolor{funGreen}{\faForward}\hspace{2mm}Pass 1: The Quick Sweep}

Go through all 30 questions. Answer the ones you know right away. Circle any that make you pause for more than 30 seconds.

\vspace{3mm}

\textbf{\textcolor{funGreen}{\faRedo}\hspace{2mm}Pass 2: The Deep Dive}

Go back to the circled questions. Now you can spend real time on them — without worrying about running out of time for the easy ones.
\end{tcolorbox}

\vspace{3mm}

\begin{tcolorbox}[
    enhanced,
    colback=funYellowLight,
    colframe=funYellow!60,
    arc=10pt,
    boxrule=1pt,
    left=6mm, right=6mm, top=4mm, bottom=4mm,
]
{\bfseries\color{funYellowDark} \faLightbulb\hspace{2mm}Try It Today}

\vspace{2mm}

Use the two-pass method on this test. After you're done, count how many answers you changed or added on the second pass. You might be surprised!
\end{tcolorbox}

\vspace{4mm}

\begin{center}
{\large\bfseries\color{funGreenDark} \faCheckDouble\hspace{2mm}Two passes, one better score.\hspace{2mm}\faCheckDouble}
\end{center}

}
\newpage
