% Pre-Test 15 — Test Day Confidence: Final simulation, trust your preparation
\clearpage
\thispagestyle{empty}
{\sffamily

\begin{center}
{\fontsize{22}{26}\selectfont\bfseries\color{funBlue} \faCrown\hspace{3mm}Your Victory Lap\hspace{3mm}\faCrown}

\vspace{2mm}
{\color{funGray}\hrulefill}
\end{center}

\vspace{3mm}

\begin{tcolorbox}[
    enhanced,
    colback=funBlueLight,
    colframe=funBlue!50,
    arc=10pt,
    boxrule=1.5pt,
    left=6mm, right=6mm, top=5mm, bottom=5mm,
]
{\large\bfseries\color{funBlueDark} \faTrophy\hspace{2mm}Test 9: The Grand Finale}

\vspace{2mm}

This is it — your last practice test. You've spent 8 tests building your skills, learning strategies, and training your brain. Now it's time to show what you can do.

\vspace{3mm}

\textbf{Before you begin, remember everything you've learned:}

\begin{itemize}[leftmargin=6mm, itemsep=3pt]
    \item[\textcolor{funBlue}{\faStar}] Two-pass method — easy first, hard second
    \item[\textcolor{funBlue}{\faStar}] Eliminate, estimate, and back-solve
    \item[\textcolor{funBlue}{\faStar}] Underline key words in each question
    \item[\textcolor{funBlue}{\faStar}] Break multi-step problems into pieces
    \item[\textcolor{funBlue}{\faStar}] Stay calm when you hit a tough one
\end{itemize}
\end{tcolorbox}

\vspace{3mm}

\begin{tcolorbox}[
    enhanced,
    colback=funYellowLight,
    colframe=funYellow!60,
    arc=10pt,
    boxrule=1pt,
    left=6mm, right=6mm, top=4mm, bottom=4mm,
]
{\bfseries\color{funYellowDark} \faLightbulb\hspace{2mm}One Last Thing}

\vspace{2mm}

You've already solved 240 math questions. Let that sink in! Walk into this test knowing you have real experience behind you. Trust the work you've put in.
\end{tcolorbox}

\vspace{4mm}

\begin{center}
{\large\bfseries\color{funBlueDark} \faRocket\hspace{2mm}Show them what 9 tests of practice looks like!\hspace{2mm}\faRocket}
\end{center}

}
\newpage
