% Pre-Test 10 — Focus & Precision: Avoiding traps, reading carefully
\clearpage
\thispagestyle{empty}
{\sffamily

\begin{center}
{\fontsize{22}{26}\selectfont\bfseries\color{funPurple} \faEye\hspace{3mm}Read Like a Detective\hspace{3mm}\faEye}

\vspace{2mm}
{\color{funGray}\hrulefill}
\end{center}

\vspace{3mm}

\begin{tcolorbox}[
    enhanced,
    colback=funPurpleLight,
    colframe=funPurple!50,
    arc=10pt,
    boxrule=1.5pt,
    left=6mm, right=6mm, top=5mm, bottom=5mm,
]
{\large\bfseries\color{funPurpleDark} \faUserSecret\hspace{2mm}Hidden Traps to Watch For}

\vspace{2mm}

Test-makers are clever. They put answer choices that \textit{look} right but aren't. Here's how to spot the traps:

\vspace{3mm}

\begin{itemize}[leftmargin=6mm, itemsep=3pt]
    \item[\textcolor{funPurple}{\faExclamationCircle}] \textbf{``NOT'' or ``EXCEPT''} — The question asks for the wrong answer. Underline these words!
    \item[\textcolor{funPurple}{\faExclamationCircle}] \textbf{Almost-right numbers} — They put the answer to a simpler version of the problem. Make sure you solved the \textit{whole} thing.
    \item[\textcolor{funPurple}{\faExclamationCircle}] \textbf{Unit switches} — The problem gives feet but asks for inches. Always check!
    \item[\textcolor{funPurple}{\faExclamationCircle}] \textbf{Partial work} — You solved step 1 of 2 and picked that answer. Finish the job!
\end{itemize}
\end{tcolorbox}

\vspace{3mm}

\begin{tcolorbox}[
    enhanced,
    colback=funYellowLight,
    colframe=funYellow!60,
    arc=10pt,
    boxrule=1pt,
    left=6mm, right=6mm, top=4mm, bottom=4mm,
]
{\bfseries\color{funYellowDark} \faLightbulb\hspace{2mm}The Underline Trick}

\vspace{2mm}

Before you solve each question, underline the \textbf{key words}: what it's asking for, any special conditions, and the units. This one habit can prevent half your mistakes.
\end{tcolorbox}

\vspace{4mm}

\begin{center}
{\large\bfseries\color{funPurpleDark} \faGem\hspace{2mm}Careful readers are confident test-takers.\hspace{2mm}\faGem}
\end{center}

}
\newpage
