% Pre-Test 13 — Resilience: Pushing through challenges, dealing with frustration
\clearpage
\thispagestyle{empty}
{\sffamily

\begin{center}
{\fontsize{22}{26}\selectfont\bfseries\color{funRed} \faFistRaised\hspace{3mm}Grit Gets You There\hspace{3mm}\faFistRaised}

\vspace{2mm}
{\color{funGray}\hrulefill}
\end{center}

\vspace{3mm}

\begin{tcolorbox}[
    enhanced,
    colback=funRedLight,
    colframe=funRed!40,
    arc=10pt,
    boxrule=1.5pt,
    left=6mm, right=6mm, top=5mm, bottom=5mm,
]
{\large\bfseries\color{funRedDark} \faHeartbeat\hspace{2mm}It's Okay to Feel Frustrated}

\vspace{2mm}

You're 7 tests into this journey. Some questions still feel hard — and that's completely normal. Even professional mathematicians get stuck. The difference? They don't give up.

\vspace{3mm}

\textbf{When frustration hits, try this:}

\vspace{2mm}

\begin{itemize}[leftmargin=6mm, itemsep=3pt]
    \item[\textcolor{funRed}{\faStar}] \textbf{Breathe.} Close your eyes for 3 seconds. Reset.
    \item[\textcolor{funRed}{\faStar}] \textbf{Move on.} Skip the question and come back fresh.
    \item[\textcolor{funRed}{\faStar}] \textbf{Talk to yourself.} Say ``I can figure this out'' — it actually works!
    \item[\textcolor{funRed}{\faStar}] \textbf{Guess smart.} Eliminate, estimate, then choose.
\end{itemize}
\end{tcolorbox}

\vspace{3mm}

\begin{tcolorbox}[
    enhanced,
    colback=funYellowLight,
    colframe=funYellow!60,
    arc=10pt,
    boxrule=1pt,
    left=6mm, right=6mm, top=4mm, bottom=4mm,
]
{\bfseries\color{funYellowDark} \faLightbulb\hspace{2mm}The 3-Question Rule}

\vspace{2mm}

If you hit 3 hard questions in a row, take a 10-second mental break. Stretch your fingers, look away from the page, then come back. A tiny reset can clear the fog.
\end{tcolorbox}

\vspace{4mm}

\begin{center}
{\large\bfseries\color{funRedDark} \faFireAlt\hspace{2mm}Tough moments make tough minds.\hspace{2mm}\faFireAlt}
\end{center}

}
\newpage
