% Pre-Test 14 — Speed + Accuracy: Balancing pace and precision
\clearpage
\thispagestyle{empty}
{\sffamily

\begin{center}
{\fontsize{22}{26}\selectfont\bfseries\color{funOrange} \faTachometerAlt\hspace{3mm}Speed Meets Accuracy\hspace{3mm}\faTachometerAlt}

\vspace{2mm}
{\color{funGray}\hrulefill}
\end{center}

\vspace{3mm}

\begin{tcolorbox}[
    enhanced,
    colback=funOrangeLight,
    colframe=funOrange!50,
    arc=10pt,
    boxrule=1.5pt,
    left=6mm, right=6mm, top=5mm, bottom=5mm,
]
{\large\bfseries\color{funOrangeDark} \faBalanceScale\hspace{2mm}Finding the Sweet Spot}

\vspace{2mm}

Going too fast? You'll make careless mistakes. Going too slow? You won't finish. The goal is to find your sweet spot — fast enough to finish, careful enough to be accurate.

\vspace{3mm}

\textbf{Today's Challenge:}

\vspace{2mm}

\textcolor{funOrange}{\faCheckCircle}\hspace{2mm}Set a timer for 40 minutes.

\vspace{2mm}

\textcolor{funOrange}{\faCheckCircle}\hspace{2mm}Try to finish all 30 questions \textit{and} check 10 of them.

\vspace{2mm}

\textcolor{funOrange}{\faCheckCircle}\hspace{2mm}If you catch a mistake while checking, celebrate — that's the system working!
\end{tcolorbox}

\vspace{3mm}

\begin{tcolorbox}[
    enhanced,
    colback=funYellowLight,
    colframe=funYellow!60,
    arc=10pt,
    boxrule=1pt,
    left=6mm, right=6mm, top=4mm, bottom=4mm,
]
{\bfseries\color{funYellowDark} \faLightbulb\hspace{2mm}Speed Tip}

\vspace{2mm}

On easy questions, trust your first instinct — don't over-think them. Save your careful thinking for the hard ones. That's how you go fast \textit{and} stay accurate.
\end{tcolorbox}

\vspace{4mm}

\begin{center}
{\large\bfseries\color{funOrangeDark} \faBolt\hspace{2mm}Quick on the easy, careful on the hard.\hspace{2mm}\faBolt}
\end{center}

}
\newpage
