% Pre-Test 09 — Working Smarter: Estimation, elimination, back-solving
\clearpage
\thispagestyle{empty}
{\sffamily

\begin{center}
{\fontsize{22}{26}\selectfont\bfseries\color{funOrange} \faToolbox\hspace{3mm}Work Smarter, Not Harder\hspace{3mm}\faToolbox}

\vspace{2mm}
{\color{funGray}\hrulefill}
\end{center}

\vspace{3mm}

\begin{tcolorbox}[
    enhanced,
    colback=funOrangeLight,
    colframe=funOrange!50,
    arc=10pt,
    boxrule=1.5pt,
    left=6mm, right=6mm, top=5mm, bottom=5mm,
]
{\large\bfseries\color{funOrangeDark} \faHatWizard\hspace{2mm}Three Power Moves}

\vspace{3mm}

\textcolor{funOrange}{\faDice}\hspace{2mm}\textbf{Estimation} — Round the numbers and do a quick mental calculation. If the answer should be ``around 45,'' an option saying ``4.5'' or ``450'' is probably wrong.

\vspace{3mm}

\textcolor{funOrange}{\faBan}\hspace{2mm}\textbf{Elimination} — Look at the four choices. Can you cross out one or two that don't make sense? Now you're choosing from 2 instead of 4!

\vspace{3mm}

\textcolor{funOrange}{\faUndoAlt}\hspace{2mm}\textbf{Back-Solving} — Start with the answer choices and plug them into the problem. When one works, that's your answer. This is especially great for equations.
\end{tcolorbox}

\vspace{3mm}

\begin{tcolorbox}[
    enhanced,
    colback=funYellowLight,
    colframe=funYellow!60,
    arc=10pt,
    boxrule=1pt,
    left=6mm, right=6mm, top=4mm, bottom=4mm,
]
{\bfseries\color{funYellowDark} \faLightbulb\hspace{2mm}Challenge Yourself}

\vspace{2mm}

During this test, try using each technique at least once. Put a small ``E,'' ``X,'' or ``B'' next to questions where you used Estimation, Elimination (X-out), or Back-solving.
\end{tcolorbox}

\vspace{4mm}

\begin{center}
{\large\bfseries\color{funOrangeDark} \faWrench\hspace{2mm}Smart strategies = more right answers.\hspace{2mm}\faWrench}
\end{center}

}
\newpage
