% Pre-Test 12 — Multi-Step Problems: Breaking complex problems into steps
\clearpage
\thispagestyle{empty}
{\sffamily

\begin{center}
{\fontsize{22}{26}\selectfont\bfseries\color{funPink} \faCubes\hspace{3mm}Breaking It Down\hspace{3mm}\faCubes}

\vspace{2mm}
{\color{funGray}\hrulefill}
\end{center}

\vspace{3mm}

\begin{tcolorbox}[
    enhanced,
    colback=funPinkLight,
    colframe=funPink!50,
    arc=10pt,
    boxrule=1.5pt,
    left=6mm, right=6mm, top=5mm, bottom=5mm,
]
{\large\bfseries\color{funPinkDark} \faPuzzlePiece\hspace{2mm}Multi-Step Problems Made Simple}

\vspace{2mm}

Some questions need two or three steps to solve. That's like building with LEGO — you don't try to snap everything together at once. You go brick by brick.

\vspace{3mm}

\textbf{The Step-by-Step Recipe:}

\vspace{2mm}

\textcolor{funPink}{\faArrowDown}\hspace{2mm}\textbf{Step 1:} Read the whole problem. What is it actually asking for?

\vspace{2mm}

\textcolor{funPink}{\faArrowDown}\hspace{2mm}\textbf{Step 2:} What information do you have? Write it down.

\vspace{2mm}

\textcolor{funPink}{\faArrowDown}\hspace{2mm}\textbf{Step 3:} What do you need to find first? Solve that.

\vspace{2mm}

\textcolor{funPink}{\faArrowDown}\hspace{2mm}\textbf{Step 4:} Use your answer from Step 3 to finish the problem.
\end{tcolorbox}

\vspace{3mm}

\begin{tcolorbox}[
    enhanced,
    colback=funYellowLight,
    colframe=funYellow!60,
    arc=10pt,
    boxrule=1pt,
    left=6mm, right=6mm, top=4mm, bottom=4mm,
]
{\bfseries\color{funYellowDark} \faLightbulb\hspace{2mm}Write It Out}

\vspace{2mm}

Use scratch paper! Writing each step keeps you organized and helps you catch mistakes. Plus, it turns a scary problem into a series of easy ones.
\end{tcolorbox}

\vspace{4mm}

\begin{center}
{\large\bfseries\color{funPinkDark} \faCube\hspace{2mm}One step at a time builds the answer.\hspace{2mm}\faCube}
\end{center}

}
\newpage
