% ============================================================================
% How Every Topic Works — Grade 7 Math Step by Step
% Visual breakdown of the step-by-step topic structure so students
% know what to expect on every page. Uses numbered tcolorbox cards
% with different accent colours.
% ============================================================================

\thispagestyle{empty}

{
\sffamily

% ── Header ────────────────────────────────────────────────────────────────
\stPageHeader{\faRoute\quad How Every Topic Works}{Every topic in this book follows the same structure.}

\vspace{-2mm}

% ── Visual breakdown cards ────────────────────────────────────────────────
\begin{center}
\begin{minipage}{0.88\textwidth}

% ── Card 1: Title & Learning Goal ──
\begin{tcolorbox}[enhanced, colback=funOrange!4, colframe=funOrange!25, arc=5pt,
    boxrule=0.6pt, left=12mm, right=6mm, top=4mm, bottom=4mm,
    overlay={\node[circle, fill=funOrange, inner sep=0pt, minimum size=22pt,
        text=white, font=\bfseries\small] at ([xshift=6mm]frame.west) {1};}]
    {\large\bfseries\color{funOrangeDark}Title \& Learning Goal}\\[2pt]
    {\color{black!55}Each topic opens with a clear title and a brief
    statement of what you will learn. This tells you the \emph{destination}
    before you start walking.}
\end{tcolorbox}

\vspace{3mm}

% ── Card 2: The Steps ──
\begin{tcolorbox}[enhanced, colback=step1Light, colframe=step1Color!25, arc=5pt,
    boxrule=0.6pt, left=12mm, right=6mm, top=4mm, bottom=4mm,
    overlay={\node[circle, fill=step1Color, inner sep=0pt, minimum size=22pt,
        text=white, font=\bfseries\small] at ([xshift=6mm]frame.west) {2};}]
    {\large\bfseries\color{step1Dark}The Steps Card}\\[2pt]
    {\color{black!55}A numbered list of every step you need. Read these
    first --- they are your roadmap. Each step is colour-coded so you can
    track it through the examples.}
\end{tcolorbox}

\vspace{3mm}

% ── Card 3: Worked Examples ──
\begin{tcolorbox}[enhanced, colback=funOrange!4, colframe=funOrange!20, arc=5pt,
    boxrule=0.6pt, left=12mm, right=6mm, top=4mm, bottom=4mm,
    overlay={\node[circle, fill=funOrange, inner sep=0pt, minimum size=22pt,
        text=white, font=\bfseries\small] at ([xshift=6mm]frame.west) {3};}]
    {\large\bfseries\color{funOrangeDark}Worked Examples}\\[2pt]
    {\color{black!55}One or more fully solved problems. Every step label
    appears in the solution so you can see \emph{exactly} where each
    step is used. Follow along with pencil and paper.}
\end{tcolorbox}

\vspace{3mm}

% ── Card 4: Your Turn ──
\begin{tcolorbox}[enhanced, colback=funYellow!4, colframe=funYellow!25, arc=5pt,
    boxrule=0.6pt, left=12mm, right=6mm, top=4mm, bottom=4mm,
    overlay={\node[circle, fill=funYellowDark!70, inner sep=0pt, minimum size=22pt,
        text=white, font=\bfseries\small] at ([xshift=6mm]frame.west) {4};}]
    {\large\bfseries\color{funYellowDark!80}Your Turn (Guided Practice)}\\[2pt]
    {\color{black!55}A problem with blanks for you to fill in, step by step.
    This is your training-wheels round --- you practise the method with
    support before going solo.}
\end{tcolorbox}

\vspace{3mm}

% ── Card 5: Practice Problems ──
\begin{tcolorbox}[enhanced, colback=funBlue!4, colframe=funBlue!25, arc=5pt,
    boxrule=0.6pt, left=12mm, right=6mm, top=4mm, bottom=4mm,
    overlay={\node[circle, fill=funBlue, inner sep=0pt, minimum size=22pt,
        text=white, font=\bfseries\small] at ([xshift=6mm]frame.west) {5};}]
    {\large\bfseries\color{funBlueDark}Practice Problems}\\[2pt]
    {\color{black!55}Independent problems to solve on your own. Answers
    are in the Answer Key at the back of the book --- always check your
    work!}
\end{tcolorbox}

\vspace{3mm}

% ── Card 6: Tips & Warnings ──
\begin{tcolorbox}[enhanced, colback=funPurple!4, colframe=funPurple!20, arc=5pt,
    boxrule=0.6pt, left=12mm, right=6mm, top=4mm, bottom=4mm,
    overlay={\node[circle, fill=funPurple, inner sep=0pt, minimum size=22pt,
        text=white, font=\bfseries\small] at ([xshift=6mm]frame.west) {6};}]
    {\large\bfseries\color{funPurpleDark}Tips \& Watch-Out Boxes}\\[2pt]
    {\color{black!55}Look for the \textcolor{funPurple}{\faLightbulb}~tip
    and \textcolor{funRed}{\faExclamationTriangle}~warning boxes ---
    they highlight common mistakes and shortcuts that save time.}
\end{tcolorbox}

\end{minipage}
\end{center}

\vspace{6mm}

% ── Bottom tip ────────────────────────────────────────────────────────────
\begin{center}
    \color{funGray}\normalsize
    \faInfoCircle\hspace{2mm}Every topic follows this same pattern.
    Once you know the rhythm, you can focus on the math.
\end{center}

}

\clearpage
