% Pre-Test 05 — Resilience: Pushing through hard problems
\clearpage
\thispagestyle{empty}
{\sffamily

\begin{center}
{\fontsize{22}{26}\selectfont\bfseries\color{funTeal} \faMountain\hspace{3mm}When the Going Gets Tough\hspace{3mm}\faMountain}

\vspace{2mm}
{\color{funGray}\hrulefill}
\end{center}

\vspace{3mm}

\begin{tcolorbox}[
    enhanced,
    colback=funTealLight,
    colframe=funTeal!50,
    arc=10pt,
    boxrule=1.5pt,
    left=6mm, right=6mm, top=5mm, bottom=5mm,
]
{\large\bfseries\color{funTealDark} \faShieldAlt\hspace{2mm}Your Resilience Game Plan}

\vspace{2mm}

Every test has a few questions that feel impossible. That's normal — they're \textit{designed} to challenge you. Here's what strong test-takers do when they hit a wall:

\vspace{3mm}

\textcolor{funTeal}{\faArrowRight}\hspace{2mm}\textbf{Step 1:} Take a breath. Feeling stuck is okay.

\vspace{2mm}

\textcolor{funTeal}{\faArrowRight}\hspace{2mm}\textbf{Step 2:} Re-read the problem. Sometimes the second read unlocks the answer.

\vspace{2mm}

\textcolor{funTeal}{\faArrowRight}\hspace{2mm}\textbf{Step 3:} Still stuck? Skip it and come back later. Your brain keeps working in the background!

\vspace{2mm}

\textcolor{funTeal}{\faArrowRight}\hspace{2mm}\textbf{Step 4:} If you're still unsure, eliminate choices and make your best guess. Never leave it blank.
\end{tcolorbox}

\vspace{3mm}

\begin{tcolorbox}[
    enhanced,
    colback=funYellowLight,
    colframe=funYellow!60,
    arc=10pt,
    boxrule=1pt,
    left=6mm, right=6mm, top=4mm, bottom=4mm,
]
{\bfseries\color{funYellowDark} \faLightbulb\hspace{2mm}Remember}

\vspace{2mm}

Getting 25 out of 30 right is awesome — even if 5 felt really hard. Don't let a tough question steal your confidence on the easy ones.
\end{tcolorbox}

\vspace{4mm}

\begin{center}
{\large\bfseries\color{funTealDark} \faMedal\hspace{2mm}Tough questions build strong minds.\hspace{2mm}\faMedal}
\end{center}

}
\newpage
