% Pre-Test 04 — Precision: Avoiding careless mistakes
\clearpage
\thispagestyle{empty}
{\sffamily

\begin{center}
{\fontsize{22}{26}\selectfont\bfseries\color{funPurple} \faSearchPlus\hspace{3mm}The Precision Challenge\hspace{3mm}\faSearchPlus}

\vspace{2mm}
{\color{funGray}\hrulefill}
\end{center}

\vspace{3mm}

\begin{tcolorbox}[
    enhanced,
    colback=funPurpleLight,
    colframe=funPurple!50,
    arc=10pt,
    boxrule=1.5pt,
    left=6mm, right=6mm, top=5mm, bottom=5mm,
]
{\large\bfseries\color{funPurpleDark} \faEye\hspace{2mm}Catch the Sneaky Mistakes}

\vspace{2mm}

Some wrong answers don't come from not knowing the math — they come from small slip-ups. Today, be a detective and watch for these common traps:

\vspace{3mm}

\begin{itemize}[leftmargin=6mm, itemsep=3pt]
    \item[\textcolor{funPurple}{\faExclamationTriangle}] \textbf{Misreading the question} — Did it ask for the \textit{least} or the \textit{greatest}?
    \item[\textcolor{funPurple}{\faExclamationTriangle}] \textbf{Sign errors} — Watch those negatives! $(-3) \times (-2) = +6$, not $-6$.
    \item[\textcolor{funPurple}{\faExclamationTriangle}] \textbf{Forgetting units} — Is the answer in feet, inches, or square units?
    \item[\textcolor{funPurple}{\faExclamationTriangle}] \textbf{Picking a partial answer} — Make sure you finished the whole problem.
\end{itemize}
\end{tcolorbox}

\vspace{3mm}

\begin{tcolorbox}[
    enhanced,
    colback=funYellowLight,
    colframe=funYellow!60,
    arc=10pt,
    boxrule=1pt,
    left=6mm, right=6mm, top=4mm, bottom=4mm,
]
{\bfseries\color{funYellowDark} \faLightbulb\hspace{2mm}The 5-Second Rule}

\vspace{2mm}

Before you lock in an answer, pause for 5 seconds. Re-read the question one more time. You'll be amazed how many mistakes this catches.
\end{tcolorbox}

\vspace{4mm}

\begin{center}
{\large\bfseries\color{funPurpleDark} \faGem\hspace{2mm}Slow down just a little. Accuracy wins.\hspace{2mm}\faGem}
\end{center}

}
\newpage
