% Pre-Test 06 — Test Day Confidence: Final simulation, you're ready
\clearpage
\thispagestyle{empty}
{\sffamily

\begin{center}
{\fontsize{22}{26}\selectfont\bfseries\color{funPink} \faTrophy\hspace{3mm}The Final Challenge\hspace{3mm}\faTrophy}

\vspace{2mm}
{\color{funGray}\hrulefill}
\end{center}

\vspace{3mm}

\begin{tcolorbox}[
    enhanced,
    colback=funPinkLight,
    colframe=funPink!50,
    arc=10pt,
    boxrule=1.5pt,
    left=6mm, right=6mm, top=5mm, bottom=5mm,
]
{\large\bfseries\color{funPinkDark} \faRocket\hspace{2mm}This Is Your Moment}

\vspace{2mm}

You've completed 5 practice tests. You've learned strategies, caught mistakes, and pushed through tough problems. Now it's time to put it all together.

\vspace{3mm}

Treat this test like the real thing:

\begin{itemize}[leftmargin=6mm, itemsep=3pt]
    \item[\textcolor{funPink}{\faStar}] Find a quiet spot with no distractions
    \item[\textcolor{funPink}{\faStar}] Set a timer if you want to simulate real conditions
    \item[\textcolor{funPink}{\faStar}] Use every strategy you've practiced
    \item[\textcolor{funPink}{\faStar}] Trust yourself — you know more than you think
\end{itemize}
\end{tcolorbox}

\vspace{3mm}

\begin{tcolorbox}[
    enhanced,
    colback=funYellowLight,
    colframe=funYellow!60,
    arc=10pt,
    boxrule=1pt,
    left=6mm, right=6mm, top=4mm, bottom=4mm,
]
{\bfseries\color{funYellowDark} \faLightbulb\hspace{2mm}Confidence Boost}

\vspace{2mm}

Think about how you felt before Test 1. Now look how far you've come! Five tests, 150 questions, and a whole toolbox of strategies. You're not the same student you were at the start.
\end{tcolorbox}

\vspace{4mm}

\begin{center}
{\large\bfseries\color{funPinkDark} \faMedal\hspace{2mm}Finish strong. You've earned this!\hspace{2mm}\faMedal}
\end{center}

}
\newpage
