% Pre-Test 01 — Foundation: First test, no pressure, establish a baseline
\clearpage
\thispagestyle{empty}
{\sffamily

\begin{center}
{\fontsize{22}{26}\selectfont\bfseries\color{funBlue} \faFlag\hspace{3mm}Welcome to Your First Test!\hspace{3mm}\faFlag}

\vspace{2mm}
{\color{funGray}\hrulefill}
\end{center}

\vspace{3mm}

\begin{tcolorbox}[
    enhanced,
    colback=funBlueLight,
    colframe=funBlue!50,
    arc=10pt,
    boxrule=1.5pt,
    left=6mm, right=6mm, top=5mm, bottom=5mm,
]
{\large\bfseries\color{funBlueDark} \faCompass\hspace{2mm}What's This All About?}

\vspace{2mm}

This first test is your starting line — not a finish line. Think of it like the first day at a new sport. Nobody expects you to score perfectly on day one!

\vspace{2mm}

Your only job right now:
\begin{itemize}[leftmargin=6mm, itemsep=3pt]
    \item[\textcolor{funBlue}{\faCheck}] Read each question carefully
    \item[\textcolor{funBlue}{\faCheck}] Try your best on every single one
    \item[\textcolor{funBlue}{\faCheck}] Don't worry about the clock
    \item[\textcolor{funBlue}{\faCheck}] Mark questions you feel unsure about
\end{itemize}
\end{tcolorbox}

\vspace{3mm}

\begin{tcolorbox}[
    enhanced,
    colback=funYellowLight,
    colframe=funYellow!60,
    arc=10pt,
    boxrule=1pt,
    left=6mm, right=6mm, top=4mm, bottom=4mm,
]
{\bfseries\color{funYellowDark} \faLightbulb\hspace{2mm}Why This Matters}

\vspace{2mm}

This test helps you figure out what you already know and what you need to practice. Every question — even the ones you get wrong — is helping you learn. Your score today is just a snapshot, not the final picture.
\end{tcolorbox}

\vspace{4mm}

\begin{center}
{\large\bfseries\color{funBlueDark} \faStar\hspace{2mm}Take a deep breath. You've got this!\hspace{2mm}\faStar}
\end{center}

}
\newpage
