% Pre-Test 03 — Techniques: Elimination, working backward, estimation
\clearpage
\thispagestyle{empty}
{\sffamily

\begin{center}
{\fontsize{22}{26}\selectfont\bfseries\color{funOrange} \faTools\hspace{3mm}Your Problem-Solving Toolkit\hspace{3mm}\faTools}

\vspace{2mm}
{\color{funGray}\hrulefill}
\end{center}

\vspace{3mm}

\begin{tcolorbox}[
    enhanced,
    colback=funOrangeLight,
    colframe=funOrange!50,
    arc=10pt,
    boxrule=1.5pt,
    left=6mm, right=6mm, top=5mm, bottom=5mm,
]
{\large\bfseries\color{funOrangeDark} \faWrench\hspace{2mm}Three Tricks for Tricky Questions}

\vspace{3mm}

\textcolor{funOrange}{\faTimesCircle}\hspace{2mm}\textbf{Eliminate Wrong Answers} — Cross out choices that are obviously wrong. Even removing one bad option boosts your odds!

\vspace{3mm}

\textcolor{funOrange}{\faUndo}\hspace{2mm}\textbf{Work Backward} — Plug the answer choices back into the problem. If one of them works, you've found it!

\vspace{3mm}

\textcolor{funOrange}{\faCalculator}\hspace{2mm}\textbf{Estimate First} — Round the numbers and do a quick mental check. This helps you spot answers that are way off.
\end{tcolorbox}

\vspace{3mm}

\begin{tcolorbox}[
    enhanced,
    colback=funYellowLight,
    colframe=funYellow!60,
    arc=10pt,
    boxrule=1pt,
    left=6mm, right=6mm, top=4mm, bottom=4mm,
]
{\bfseries\color{funYellowDark} \faLightbulb\hspace{2mm}Try It Today}

\vspace{2mm}

Pick at least \textbf{3 questions} during this test where you use one of these tricks. See how it feels — you might surprise yourself!
\end{tcolorbox}

\vspace{4mm}

\begin{center}
{\large\bfseries\color{funOrangeDark} \faHammer\hspace{2mm}The right tool makes every problem easier.\hspace{2mm}\faHammer}
\end{center}

}
\newpage
