% Post-Test 27 — Complete Journey: 360 questions, full celebration, readiness
\clearpage
\thispagestyle{empty}
{\sffamily

\begin{center}
{\fontsize{22}{26}\selectfont\bfseries\color{funTeal} \faTrophy\hspace{3mm}You Did It!\hspace{3mm}\faTrophy}

\vspace{2mm}
{\color{funGray}\hrulefill}
\end{center}

\vspace{3mm}

\begin{tcolorbox}[
    enhanced,
    colback=funTealLight,
    colframe=funTeal!50,
    arc=10pt,
    boxrule=1.5pt,
    left=6mm, right=6mm, top=5mm, bottom=5mm,
]
{\large\bfseries\color{funTealDark} \faCrown\hspace{2mm}360 Questions Complete!}

\vspace{2mm}

You just finished \textbf{360 practice questions} across \textbf{12 full tests}. That's an incredible achievement. Take a moment to appreciate how much effort, focus, and determination that took.

\vspace{3mm}

\textbf{Look how much you've grown:}

\vspace{2mm}

\hspace{3mm}\textcolor{funTeal}{\faStar}\hspace{2mm}Test 1 score: \rule[-2pt]{1.2cm}{0.5pt}/30 \hfill Test 12 score: \rule[-2pt]{1.2cm}{0.5pt}/30

\vspace{2mm}

\hspace{3mm}\textcolor{funTeal}{\faStar}\hspace{2mm}Total improvement: \rule[-2pt]{2cm}{0.5pt} points

\vspace{2mm}

\hspace{3mm}\textcolor{funTeal}{\faStar}\hspace{2mm}My best score: \rule[-2pt]{2cm}{0.5pt}/30

\vspace{2mm}

\hspace{3mm}\textcolor{funTeal}{\faStar}\hspace{2mm}I'm most proud of: \rule[-2pt]{6cm}{0.5pt}
\end{tcolorbox}

\vspace{3mm}

\begin{tcolorbox}[
    enhanced,
    colback=funGreenLight,
    colframe=funGreen!50,
    arc=10pt,
    boxrule=1pt,
    left=6mm, right=6mm, top=4mm, bottom=4mm,
]
{\bfseries\color{funGreenDark} \faGraduationCap\hspace{2mm}You Are Ready}

\vspace{2mm}

Whether your goal was to crush a state exam, build confidence, or master 7th grade math — you've put in the work. Twelve tests is no joke. You are more prepared today than you have ever been. Walk into that test room and show them what you've got!
\end{tcolorbox}

\vspace{4mm}

\begin{center}
{\large\bfseries\color{funTealDark} \faAward\hspace{2mm}Champion in the making. Go shine!\hspace{2mm}\faAward}
\end{center}

}
\newpage
