% Pre-Test 22 — Multi-Step Problems: Breaking complex problems into pieces
\clearpage
\thispagestyle{empty}
{\sffamily

\begin{center}
{\fontsize{22}{26}\selectfont\bfseries\color{funRed} \faCubes\hspace{3mm}Conquer Multi-Step Problems\hspace{3mm}\faCubes}

\vspace{2mm}
{\color{funGray}\hrulefill}
\end{center}

\vspace{3mm}

\begin{tcolorbox}[
    enhanced,
    colback=funRedLight,
    colframe=funRed!40,
    arc=10pt,
    boxrule=1.5pt,
    left=6mm, right=6mm, top=5mm, bottom=5mm,
]
{\large\bfseries\color{funRedDark} \faProjectDiagram\hspace{2mm}Big Problems = Small Steps}

\vspace{2mm}

The hardest questions on any test are usually multi-step problems. They look scary, but they're really just 2 or 3 easy problems stacked together. Here's how to unstack them:

\vspace{3mm}

\textcolor{funRed}{\faArrowDown}\hspace{2mm}\textbf{Identify} — What does the question ask for? Write it down.

\vspace{2mm}

\textcolor{funRed}{\faArrowDown}\hspace{2mm}\textbf{List} — What information do you have? What's missing?

\vspace{2mm}

\textcolor{funRed}{\faArrowDown}\hspace{2mm}\textbf{Solve the first piece} — Find the missing value you need.

\vspace{2mm}

\textcolor{funRed}{\faArrowDown}\hspace{2mm}\textbf{Use it} — Plug your answer into the next step.

\vspace{2mm}

\textcolor{funRed}{\faArrowDown}\hspace{2mm}\textbf{Check} — Does your final answer make sense?
\end{tcolorbox}

\vspace{3mm}

\begin{tcolorbox}[
    enhanced,
    colback=funYellowLight,
    colframe=funYellow!60,
    arc=10pt,
    boxrule=1pt,
    left=6mm, right=6mm, top=4mm, bottom=4mm,
]
{\bfseries\color{funYellowDark} \faLightbulb\hspace{2mm}Key Tip}

\vspace{2mm}

Number your steps on scratch paper: Step 1, Step 2, Step 3. This keeps you from losing track in the middle of a long problem.
\end{tcolorbox}

\vspace{4mm}

\begin{center}
{\large\bfseries\color{funRedDark} \faPuzzlePiece\hspace{2mm}Brick by brick, you build the answer.\hspace{2mm}\faPuzzlePiece}
\end{center}

}
\newpage
