% Pre-Test 19 — Process of Elimination: Strategic guessing, narrow choices
\clearpage
\thispagestyle{empty}
{\sffamily

\begin{center}
{\fontsize{22}{26}\selectfont\bfseries\color{funPurple} \faTimesCircle\hspace{3mm}The Power of Elimination\hspace{3mm}\faTimesCircle}

\vspace{2mm}
{\color{funGray}\hrulefill}
\end{center}

\vspace{3mm}

\begin{tcolorbox}[
    enhanced,
    colback=funPurpleLight,
    colframe=funPurple!50,
    arc=10pt,
    boxrule=1.5pt,
    left=6mm, right=6mm, top=5mm, bottom=5mm,
]
{\large\bfseries\color{funPurpleDark} \faCut\hspace{2mm}Cross Out the Imposters}

\vspace{2mm}

You don't always need to know the right answer — sometimes it's easier to spot the wrong ones! Here's how:

\vspace{3mm}

\textcolor{funPurple}{\faArrowRight}\hspace{2mm}\textbf{Too big or too small?} If you estimate the answer is around 50, you can cross out 5 and 500 right away.

\vspace{2mm}

\textcolor{funPurple}{\faArrowRight}\hspace{2mm}\textbf{Wrong sign?} If the answer should be positive, eliminate negatives.

\vspace{2mm}

\textcolor{funPurple}{\faArrowRight}\hspace{2mm}\textbf{Doesn't make sense?} If a distance question has a negative answer, that's impossible. Cross it out!

\vspace{2mm}

\textcolor{funPurple}{\faArrowRight}\hspace{2mm}\textbf{Down to two?} You just doubled your chance of getting it right. Make your best choice and move on.
\end{tcolorbox}

\vspace{3mm}

\begin{tcolorbox}[
    enhanced,
    colback=funYellowLight,
    colframe=funYellow!60,
    arc=10pt,
    boxrule=1pt,
    left=6mm, right=6mm, top=4mm, bottom=4mm,
]
{\bfseries\color{funYellowDark} \faLightbulb\hspace{2mm}Today's Goal}

\vspace{2mm}

On every question where you're unsure, physically cross out at least one answer choice before picking. Draw an X right through it!
\end{tcolorbox}

\vspace{4mm}

\begin{center}
{\large\bfseries\color{funPurpleDark} \faGem\hspace{2mm}Eliminate the wrong to find the right.\hspace{2mm}\faGem}
\end{center}

}
\newpage
