% Pre-Test 16 — Marathon Mindset: 12 tests is a marathon, no pressure on test 1
\clearpage
\thispagestyle{empty}
{\sffamily

\begin{center}
{\fontsize{22}{26}\selectfont\bfseries\color{funBlue} \faRunning\hspace{3mm}The Marathon Begins\hspace{3mm}\faRunning}

\vspace{2mm}
{\color{funGray}\hrulefill}
\end{center}

\vspace{3mm}

\begin{tcolorbox}[
    enhanced,
    colback=funBlueLight,
    colframe=funBlue!50,
    arc=10pt,
    boxrule=1.5pt,
    left=6mm, right=6mm, top=5mm, bottom=5mm,
]
{\large\bfseries\color{funBlueDark} \faRoad\hspace{2mm}12 Tests. One Amazing Journey.}

\vspace{2mm}

Welcome! You're about to embark on 12 practice tests — that's 360 questions and a whole lot of learning. Think of this like training for a big race: you wouldn't sprint the first mile of a marathon.

\vspace{3mm}

\textbf{Today's only mission:}

\begin{itemize}[leftmargin=6mm, itemsep=3pt]
    \item[\textcolor{funBlue}{\faPencilAlt}] Try every question — don't leave any blank
    \item[\textcolor{funBlue}{\faPencilAlt}] Take your time — no clock today
    \item[\textcolor{funBlue}{\faPencilAlt}] Mark questions that feel hard with a star
    \item[\textcolor{funBlue}{\faPencilAlt}] Be curious, not worried
\end{itemize}
\end{tcolorbox}

\vspace{3mm}

\begin{tcolorbox}[
    enhanced,
    colback=funYellowLight,
    colframe=funYellow!60,
    arc=10pt,
    boxrule=1pt,
    left=6mm, right=6mm, top=4mm, bottom=4mm,
]
{\bfseries\color{funYellowDark} \faLightbulb\hspace{2mm}Marathon Mindset}

\vspace{2mm}

Your first test is just the warm-up. No matter what you score, you have 11 more tests to learn and grow. The only thing that matters today is starting.
\end{tcolorbox}

\vspace{4mm}

\begin{center}
{\large\bfseries\color{funBlueDark} \faFlagCheckered\hspace{2mm}Mile one. Let's go!\hspace{2mm}\faFlagCheckered}
\end{center}

}
\newpage
