% Pre-Test 24 — Mid-Journey Checkpoint: Pause, reflect, reset for home stretch
\clearpage
\thispagestyle{empty}
{\sffamily

\begin{center}
{\fontsize{22}{26}\selectfont\bfseries\color{funBlue} \faMapMarkedAlt\hspace{3mm}Mid-Journey Checkpoint\hspace{3mm}\faMapMarkedAlt}

\vspace{2mm}
{\color{funGray}\hrulefill}
\end{center}

\vspace{3mm}

\begin{tcolorbox}[
    enhanced,
    colback=funBlueLight,
    colframe=funBlue!50,
    arc=10pt,
    boxrule=1.5pt,
    left=6mm, right=6mm, top=5mm, bottom=5mm,
]
{\large\bfseries\color{funBlueDark} \faCompass\hspace{2mm}Look How Far You've Come}

\vspace{2mm}

Pause for a moment. You're about to take test 9 of 12. That means you've already answered \textbf{240 questions}! Here's what you've learned along the way:

\vspace{3mm}

\begin{itemize}[leftmargin=6mm, itemsep=3pt]
    \item[\textcolor{funBlue}{\faStar}] How to read questions like a detective
    \item[\textcolor{funBlue}{\faStar}] The two-pass method
    \item[\textcolor{funBlue}{\faStar}] Process of elimination
    \item[\textcolor{funBlue}{\faStar}] Showing your work and drawing diagrams
    \item[\textcolor{funBlue}{\faStar}] Breaking multi-step problems into pieces
    \item[\textcolor{funBlue}{\faStar}] Managing your time
\end{itemize}

\vspace{2mm}

That's a serious toolkit!
\end{tcolorbox}

\vspace{3mm}

\begin{tcolorbox}[
    enhanced,
    colback=funYellowLight,
    colframe=funYellow!60,
    arc=10pt,
    boxrule=1pt,
    left=6mm, right=6mm, top=4mm, bottom=4mm,
]
{\bfseries\color{funYellowDark} \faLightbulb\hspace{2mm}Reset and Recharge}

\vspace{2mm}

The home stretch is 4 tests away. Take a breath, shake off any frustration from earlier tests, and approach this one with fresh energy. The best is yet to come!
\end{tcolorbox}

\vspace{4mm}

\begin{center}
{\large\bfseries\color{funBlueDark} \faMountain\hspace{2mm}Three-quarters of the way up. Keep climbing!\hspace{2mm}\faMountain}
\end{center}

}
\newpage
