% Pre-Test 26 — Speed + Precision: Balancing accuracy and pace
\clearpage
\thispagestyle{empty}
{\sffamily

\begin{center}
{\fontsize{22}{26}\selectfont\bfseries\color{funPurple} \faBolt\hspace{3mm}Fast and Flawless\hspace{3mm}\faBolt}

\vspace{2mm}
{\color{funGray}\hrulefill}
\end{center}

\vspace{3mm}

\begin{tcolorbox}[
    enhanced,
    colback=funPurpleLight,
    colframe=funPurple!50,
    arc=10pt,
    boxrule=1.5pt,
    left=6mm, right=6mm, top=5mm, bottom=5mm,
]
{\large\bfseries\color{funPurpleDark} \faBalanceScaleLeft\hspace{2mm}The Speed-Accuracy Balance}

\vspace{2mm}

You've practiced going fast. You've practiced being careful. Now let's combine them into one smooth performance:

\vspace{3mm}

\textbf{Your test personality today:}

\vspace{2mm}

\begin{itemize}[leftmargin=6mm, itemsep=3pt]
    \item[\textcolor{funPurple}{\faBolt}] \textbf{Easy questions} — Trust your gut. Solve quickly. Don't over-think.
    \item[\textcolor{funPurple}{\faEye}] \textbf{Medium questions} — Work through them, write your steps, pick carefully.
    \item[\textcolor{funPurple}{\faShieldAlt}] \textbf{Hard questions} — Slow down. Eliminate wrong choices. Use every strategy you know.
\end{itemize}

\vspace{2mm}

The key is knowing \textit{which mode to use} for each question. That's what separates good test-takers from great ones.
\end{tcolorbox}

\vspace{3mm}

\begin{tcolorbox}[
    enhanced,
    colback=funYellowLight,
    colframe=funYellow!60,
    arc=10pt,
    boxrule=1pt,
    left=6mm, right=6mm, top=4mm, bottom=4mm,
]
{\bfseries\color{funYellowDark} \faLightbulb\hspace{2mm}The 35-Minute Challenge}

\vspace{2mm}

Set a timer for 35 minutes. Can you finish \textit{and} have time to review a few answers? That's the sweet spot you're aiming for on test day.
\end{tcolorbox}

\vspace{4mm}

\begin{center}
{\large\bfseries\color{funPurpleDark} \faTachometerAlt\hspace{2mm}Speed where you can. Precision where it counts.\hspace{2mm}\faTachometerAlt}
\end{center}

}
\newpage
