% Pre-Test 25 — Avoiding Common Traps: Error prevention, trick questions
\clearpage
\thispagestyle{empty}
{\sffamily

\begin{center}
{\fontsize{22}{26}\selectfont\bfseries\color{funGreen} \faShieldAlt\hspace{3mm}Dodge the Traps\hspace{3mm}\faShieldAlt}

\vspace{2mm}
{\color{funGray}\hrulefill}
\end{center}

\vspace{3mm}

\begin{tcolorbox}[
    enhanced,
    colback=funGreenLight,
    colframe=funGreen!50,
    arc=10pt,
    boxrule=1.5pt,
    left=6mm, right=6mm, top=5mm, bottom=5mm,
]
{\large\bfseries\color{funGreenDark} \faExclamationTriangle\hspace{2mm}Top 5 Traps — and How to Avoid Them}

\vspace{3mm}

\textcolor{funGreen}{\faArrowRight}\hspace{2mm}\textbf{Trap 1: The ``Almost'' Answer} — You solved 80\% of the problem and picked that number. Always finish every step.

\vspace{2mm}

\textcolor{funGreen}{\faArrowRight}\hspace{2mm}\textbf{Trap 2: Negative Switch} — $(-4)^2 = 16$, not $-16$. Parentheses matter!

\vspace{2mm}

\textcolor{funGreen}{\faArrowRight}\hspace{2mm}\textbf{Trap 3: Unit Mismatch} — The problem says meters, the answer should be in centimeters. Convert!

\vspace{2mm}

\textcolor{funGreen}{\faArrowRight}\hspace{2mm}\textbf{Trap 4: ``Which is NOT''} — You found a true statement when they asked for the false one. Re-read!

\vspace{2mm}

\textcolor{funGreen}{\faArrowRight}\hspace{2mm}\textbf{Trap 5: Decimal Slide} — $0.3 \times 0.2 = 0.06$, not $0.6$. Count those decimal places.
\end{tcolorbox}

\vspace{3mm}

\begin{tcolorbox}[
    enhanced,
    colback=funYellowLight,
    colframe=funYellow!60,
    arc=10pt,
    boxrule=1pt,
    left=6mm, right=6mm, top=4mm, bottom=4mm,
]
{\bfseries\color{funYellowDark} \faLightbulb\hspace{2mm}Your Anti-Trap Checklist}

\vspace{2mm}

Before picking your answer: Did I finish the problem? Are my signs right? Are my units right? Did I read the question correctly? If yes to all four — lock it in!
\end{tcolorbox}

\vspace{4mm}

\begin{center}
{\large\bfseries\color{funGreenDark} \faShieldAlt\hspace{2mm}Awareness is your best defense.\hspace{2mm}\faShieldAlt}
\end{center}

}
\newpage
