% Pre-Test 17 — Read Like a Detective: Careful reading, understand the question
\clearpage
\thispagestyle{empty}
{\sffamily

\begin{center}
{\fontsize{22}{26}\selectfont\bfseries\color{funGreen} \faUserSecret\hspace{3mm}Read Like a Detective\hspace{3mm}\faUserSecret}

\vspace{2mm}
{\color{funGray}\hrulefill}
\end{center}

\vspace{3mm}

\begin{tcolorbox}[
    enhanced,
    colback=funGreenLight,
    colframe=funGreen!50,
    arc=10pt,
    boxrule=1.5pt,
    left=6mm, right=6mm, top=5mm, bottom=5mm,
]
{\large\bfseries\color{funGreenDark} \faSearch\hspace{2mm}The Clues Are in the Question}

\vspace{2mm}

A detective doesn't glance at the crime scene and make a guess. They look at every detail. That's how you should read test questions too!

\vspace{3mm}

\textbf{Your 3-Step Reading Method:}

\vspace{2mm}

\textcolor{funGreen}{\faGlasses}\hspace{2mm}\textbf{Read 1:} Read the whole question to get the big picture.

\vspace{2mm}

\textcolor{funGreen}{\faHighlighter}\hspace{2mm}\textbf{Read 2:} Underline the key numbers and the question itself.

\vspace{2mm}

\textcolor{funGreen}{\faCheckDouble}\hspace{2mm}\textbf{Read 3:} Before picking your answer, re-read the last sentence. ``What is it actually asking?''
\end{tcolorbox}

\vspace{3mm}

\begin{tcolorbox}[
    enhanced,
    colback=funYellowLight,
    colframe=funYellow!60,
    arc=10pt,
    boxrule=1pt,
    left=6mm, right=6mm, top=4mm, bottom=4mm,
]
{\bfseries\color{funYellowDark} \faLightbulb\hspace{2mm}Watch Out For These Words}

\vspace{2mm}

\textbf{NOT, EXCEPT, LEAST, GREATEST, APPROXIMATELY, BEST.} These words change everything! Circle them whenever you spot one.
\end{tcolorbox}

\vspace{4mm}

\begin{center}
{\large\bfseries\color{funGreenDark} \faSearch\hspace{2mm}Read carefully. Solve confidently.\hspace{2mm}\faSearch}
\end{center}

}
\newpage
