% Pre-Test 27 — Test Day Ready: Final simulation under real conditions
\clearpage
\thispagestyle{empty}
{\sffamily

\begin{center}
{\fontsize{22}{26}\selectfont\bfseries\color{funTeal} \faTrophy\hspace{3mm}The Grand Finale\hspace{3mm}\faTrophy}

\vspace{2mm}
{\color{funGray}\hrulefill}
\end{center}

\vspace{3mm}

\begin{tcolorbox}[
    enhanced,
    colback=funTealLight,
    colframe=funTeal!50,
    arc=10pt,
    boxrule=1.5pt,
    left=6mm, right=6mm, top=5mm, bottom=5mm,
]
{\large\bfseries\color{funTealDark} \faRocket\hspace{2mm}This Is It — Test 12 of 12}

\vspace{2mm}

You started as someone taking their first practice test. Now you're a battle-tested math warrior with \textbf{11 tests of experience} behind you. That's \textbf{330 questions solved}!

\vspace{3mm}

Make this feel like the real thing:

\begin{itemize}[leftmargin=6mm, itemsep=3pt]
    \item[\textcolor{funTeal}{\faStar}] Sit at a desk in a quiet room
    \item[\textcolor{funTeal}{\faStar}] Put your phone away
    \item[\textcolor{funTeal}{\faStar}] Set a timer for test conditions
    \item[\textcolor{funTeal}{\faStar}] Have scratch paper and a pencil ready
    \item[\textcolor{funTeal}{\faStar}] Use every strategy in your toolkit
\end{itemize}
\end{tcolorbox}

\vspace{3mm}

\begin{tcolorbox}[
    enhanced,
    colback=funYellowLight,
    colframe=funYellow!60,
    arc=10pt,
    boxrule=1pt,
    left=6mm, right=6mm, top=4mm, bottom=4mm,
]
{\bfseries\color{funYellowDark} \faLightbulb\hspace{2mm}Your Final Pep Talk}

\vspace{2mm}

Think about how nervous you felt before Test 1. Now think about all the strategies you've mastered, the patterns you've spotted, and the mistakes you've learned from. You're not the same student. Trust the work you've done. Go be amazing.
\end{tcolorbox}

\vspace{4mm}

\begin{center}
{\large\bfseries\color{funTealDark} \faMedal\hspace{2mm}Finish strong. You've earned every bit of this.\hspace{2mm}\faMedal}
\end{center}

}
\newpage
